### 2008-10-22 trunk/Latex/H2Preview/H2Prev2norm.tex
DJNL written conclusions

We now turn our attention to the evaluation of $\nrm{T_{r\rightarrow z}}_2$. Since the signal $r$ is `known' to the controller, it does not introduce an estimation error. As a result the output feedback controller achieves exactly the same transfer function $T_{r\rightarrow z}$ as the full-information controller, $K_{FI}$. Thus:
\als{
T_{r\rightarrow z}=\ssmodf{A+B_2F_2}{\ma{B_{2g}F_{0r}\\B_p}}{C_1+D_{12}F_2}{D_{12}F_{0r}}.
}
%
Note that $X$ satisfies: 
\als{(A+B_2F_2)'X(A+B_2F_2)+(C_1+D_{12}F_2)'(C_1+D_{12}F_2),}
and so using equation (\ref{eqn:2normcomp}) we may write:
\als{
\nrm{T_{r\rightarrow z}}^2_2 &=\tra{\left(D_{12}F_{0r}\right)'D_{12}F_{0r}+\ma{B_{2g}F_{0r}\\B_p}'\ma{X_{gg}&X_{gp}\\X_{gp}'&X_{pp}}\ma{B_{2g}F_{0r}\\B_p}}.
} 
\mbox{where $F_{0r}=-{\bar R}^{-1}B_{2g}'X_{gp}B_p$. The above expression may be simplified to} 
\aln{
\nrm{T_{r\rightarrow z}}^2_2&=\tra{B_p'X_{pp}B_p-F_{0r}'\bar RF_{0r}\label{eqn:gamrmedeff}}.
}
%
Our next task is to find an efficient method for computing $B_p'X_{pp}B_p$. Using the $W_r=I$ version of (\ref{eqn:Xdd}), we can write:
\als{
X_{pp}&=A_p'X_{pp}A_p+\hat Q-F_{2p}'\bar{R}F_{2p}\\
\mbox{in which} \\
\hat Q &= C_{p}'B_{1gr}'X_{gg}B_{1gr}C_{p}+A_p'X_{gp}'B_{1gr}C_{p}+C_{p}'B_{1gr}'X_{gp}A_p+C_{p}'D_{11gr}'D_{11gr}C_{p}.
}

Substituting this into itself leads to:

\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\aln{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{Zero preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
\label{eqn:H2CostSplit}}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Comparing this to (\ref{eqn:H2CostSplit}), it follows that the reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is bounded above by 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation (in addition to the $n_g$ dimensional DARE required to evaluate $S$). The following quantity provides a useful measure of the fraction of the maximum norm reduction that has been achieved:
\aln{\gamma_{\,_{\%,imp}}=100\times \tra{S'\Gamma S}^{-1}{\left(\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S\right)}.\label{eqn:gamimp}} 
%This provides a useful bound on the achievable norm reduction one might obtain using preview. 
This can be used to determine how much preview to use; for example, one might continue adding preview points until $\gamma_{\,_{\%,imp}} >99\%$.

>>>>

We now turn our attention to the evaluation of $\nrm{T_{r\rightarrow z}}_2$. Since the signal $r$ is `known' to the controller, it does not introduce an estimation error. As a result the output feedback controller achieves exactly the same transfer function $T_{r\rightarrow z}$ as the full-information controller, $K_{FI}$. Thus:
\als{
T_{r\rightarrow z}=\ssmodf{A+B_2F_2}{\ma{B_{2g}F_{0r}\\B_p}}{C_1+D_{12}F_2}{D_{12}F_{0r}}.
}
%
Note that $X$ satisfies: 
\als{(A+B_2F_2)'X(A+B_2F_2)+(C_1+D_{12}F_2)'(C_1+D_{12}F_2),}
and so using equation (\ref{eqn:2normcomp}) we may write:
\als{
\nrm{T_{r\rightarrow z}}^2_2 &=\tra{\left(D_{12}F_{0r}\right)'D_{12}F_{0r}+\ma{B_{2g}F_{0r}\\B_p}'\ma{X_{gg}&X_{gp}\\X_{gp}'&X_{pp}}\ma{B_{2g}F_{0r}\\B_p}}.
} 
\mbox{where $F_{0r}=-{\bar R}^{-1}B_{2g}'X_{gp}B_p$. The above expression may be simplified to} 
\aln{
\nrm{T_{r\rightarrow z}}^2_2&=\tra{B_p'X_{pp}B_p-F_{0r}'\bar RF_{0r}\label{eqn:gamrmedeff}}.
}
%
Our next task is to find an efficient method for computing $B_p'X_{pp}B_p$. Using the $W_r=I$ version of (\ref{eqn:Xdd}), we can write:
\als{
X_{pp}&=A_p'X_{pp}A_p+\hat Q-F_{2p}'\bar{R}F_{2p}}
in which
\als{
\hat Q &= C_{p}'B_{1gr}'X_{gg}B_{1gr}C_{p}+A_p'X_{gp}'B_{1gr}C_{p}+C_{p}'B_{1gr}'X_{gp}A_p+C_{p}'D_{11gr}'D_{11gr}C_{p}.
}
Substituting this into itself leads to:
\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\aln{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{Zero preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
\label{eqn:H2CostSplit}}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Comparing this to (\ref{eqn:H2CostSplit}), it follows that the maximum reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is given by: 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation (in addition to the $n_g$ dimensional DARE required to evaluate $S$). The following quantity provides a useful measure of the fraction of the maximum norm reduction that has been achieved:
\aln{\gamma_{\,_{\%,imp}}=100\times \tra {\left(\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S\right)} / \tra{S'\Gamma S}.\label{eqn:gamimp}} 
%This provides a useful bound on the achievable norm reduction one might obtain using preview. 
This can be used to determine how much preview to use; for example, one might continue adding preview points until $\gamma_{\,_{\%,imp}} >95 \%$.

### 2008-10-22 trunk/Latex/H2Preview/H2PrevConcs.tex
DJNL written conclusions

\label{sec:Conclusions}
Preview control has been studied for over three decades and many theoretical results can be found in the technical literature. Preview control has also been employed in a variety of contempory applications in mechanical engineering. These include active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}. The purpose of the present work is to embed a class of preview control problems in a generalized regulator configuration \cite{LimebeerGreen,ZDG}. The open-loop system is controlled by a two-degree-of-freedom controller, which optimizes the system response to a combination of previewable and non-previewable exogenous inputs. Efficient algorithms have been presented for solving the two standard LQG Riccati equations, as well as computing the perfect information controller gains. The associated state estimator is low order with degree $n_g+n_r$. A detailed analysis of the achievable $\htwo$-norm cost reduction due to preview is also presented. The paper concludes with a summary of the main features of $\htwo$ preview control as well as some useful design insights.

>>>>

\label{sec:Conclusions}
Preview control has been studied for at least four decades and a large number of theoretical results can be found in the control and mechanical engineering technical literature. In many cases the theoretical developments on discrete-time $\htwo$/LQG were driven by applications problems. Contemporary applications include for example active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}.
Other applications examples, which are also related to vehicle dynamics problems, can be found in the first author's thesis; visit \url{http://code.google.com/p/preview-control-toolbox/}. A MATLAB Preview Control toolbox implementation of the presented algorithms together with their $\hinf$ counterpart can also be obtained this site.

In the authors' opinion the strong influence of applications problems has produced a body of theory that is example-specific and consequently somewhat restricted in terms of its scope and generality. To the best of our knowledge a complete set of tools for synthesising $\htwo$ preview controllers that solve broad range of realistic design problems is unavailable in the open literature. The provision of these tools is the central purpose of the work presented here. We present a general preview problem that captures most of the results in the contemporary literature, as well as offering a solution framework for more complex preview problems such as the preview tracking with integral action problem illustrated in Figure \ref{fig:TrackSysIntegDesign}.

The preview control problem studied in this paper is shown in Figure~\ref{fig:DistRejSys}, and  comprises a plant that is controlled by a two-degree-of-freedom controller. The controller is synthesized to optimize the closed-loop system's response to a combination of previewable and non-previewable exogenous inputs.  The presented solution includes an efficient computational framework that is based on two low-order Riccati equations with dimension that of the plant (excluding the preview delay line). This algorithm also includes an efficient computation of the perfect information controller gains as well as the controller itself. We have also provided an efficient method for finding the $\htwo$ norm of the closed-loop system, and a method for evaluating the norm reduction due to preview as $N \rightarrow \infty$. As is shown in Figures~\ref{fig:PrevContStruct} and \ref{fig:PrevContStructxp}, the controller structure is essentially low order with the preview part implemented using an efficient finite-impulse-response section.

### 2008-10-22 trunk/Latex/H2Preview/H2PrevIntro.tex
DJNL written conclusions

\label{sec:Intro}
There are many situations in which reference signals, or future disturbances are `previewable'. 
Optimal Preview Control is concerned with designing controllers that exploit previewed information in order to achieve performance levels that are superior to those achievable using current information alone. This paper considers the generic preview synthesis problem illustrated in Figure \ref{fig:DistRejSys}, which comprises a two-degree-of-freedom controller and both previewed disturbances/references ($r$), and unpreviewed disturbances ($w$).
An $\htwo$-optimal solution to this controller synthesis problem is provided that requires only low-dimensional computations and low-dimensional Riccati equation solutions, and leads to a controller whose high-dimensional component is a Finite Impulse Response (FIR) filter; the efficient implementation of FIR filters is well known is the signal processing literature.
The low-dimensional solution to the problem described in Figure~\ref{fig:DistRejSys} derives from the fact that the states of the (high-dimensional) delay line can be reconstructed by making a copy of $\Phi$ in the controller.  The objective of this paper is to provide a framework for synthesizing preview controllers for any problem that fits into the framework illustrated in Figure~\ref{fig:DistRejSys}. In addition, we aim to provide some general insights into the design of preview controllers, and a method for assessing the effectiveness of preview in terms of the achievable $\htwo$-norm reduction.
\begin{figure}
\begin{center}
\stdcontrolfrags
\psfrag{Phi}{$\Phi$}
\psfrag{r}{$r$}
\psfrag{rhat}{$\hat r$}
\psfrag{eta}{$\eta$}
\psfrag{G_p}{$G_p$}
\includegraphics[height=4.0cm]{./diags/DistRejSys.eps}
\caption{\label{fig:DistRejSys} A generalized regulator problem with both previewable and non-previewable disturbances. The transfer function $G$ is the system to be controlled, $K$ is the controller to be synthesized and $\Phi$ is an $N$-step delay line. The disturbance $w$ is not previewable, the control and measurement signals are $u$ and $y$ respectively, $\hat r$ is the previewable disturbance, and $r$ is the future value of $\hat r$. The filter $W_r$ is used  model the expected frequency content of $r$.}
\end{center}
\end{figure}

@@

Figure~\ref{fig:SimpleSISOPrev} illustrates a simple example that may be used to highlight the benefit of preview, the broad structure of the controller, and the effect of preview on the achievable $\htwo$-norm of the closed-loop system. In this formulation, the preview action arises because of the delay line $\Phi$. The input to the controller is $r$, which is the future value of the reference, and $K$ is chosen so as to ensure that $e$ is `small', and hence the plant output follows $\Phi r$ as closely as possible. 
\begin{figure}
\stdcontrolfrags
\begin{center}
\includegraphics[width=0.4\hsize]{./diags/SimpleExampleNominalNoK2.eps}
\end{center}
\caption{A simple SISO open-loop preview tracking problem. The transfer function $\Phi=\z^{-N}$ is an $N$-step delay, $G$ is the plant to be controlled, and $K$ is a feedforward controller. The signal $r$ is the \textit{future} value of the reference, and $e$ is the tracking error.}
\label{fig:SimpleSISOPrev}
\end{figure}
%
Now define the error system:
\als{E(\z)=G(\z)K(\z)-\Phi(\z),}
and assume that $G(\z)$ is stable; in the case that $G(\z)$ is unstable, it could be replaced by $\hat G(\z)=G(\z)(1-G(\z)K_f(\z))^{-1}$ in which $K_f(\z)$ is a stabilising feedback controller. Providing that $G(\z)$ has all its zeros inside the unit circle, perfect tracking ($E(\z)=0$) may be achieved by simply setting $K(\z)=G(\z)^{-1}\Phi(\z)$. 
However, if $G(\z)$ is {NMP}, then such a $K(\z)$ is not internally stabilising and a controller must be found that recognises the limits imposed by {NMP} zeros on the achievable tracking performance. %Such limitations are well known for non-preview systems (i.e. $N=0$ and $\Phi=1$), and are investigated in some detail in \cite{Middleteon_2004_PrevPerf} and \cite{Mirkin_2004_FixedLagPerfSaturation} for the preview case.

For the case where $G(\z)$ is an arbitrary stable, rational transfer function having a single real {NMP} zero at $c_z$, an algebraic expression for the $\htwo$-optimal controller will now be found. Our objective is to find an internally stabilising $K(\z)$ such that $\nrm{E(\z)}_2$ is minimised.

The following inner-outer factorization  may be performed:
\als{G(\z)&= G_o(\z) G_i(\z),
\intertext{where: }
G_i(\z)&=\frac{\z-c_z}{1-\z c_z}
.}
We can write $E(\z)= (\tilde{K}(\z) -\Phi(\z)G_i(\z^{-1}))G_i(\z)$ in which $\tilde{K}(\z)= K(\z) G_o(\z)$ and:
\mbox{$G_i(\z^{-1})G_i(\z)=1$}. The optimal controller is found by setting $K(\z) = (\Phi(\z)G_i(\z^{-1}))_+ G_o^{-1}(\z) $, where $(\cdot)_+$ denotes the stable projection \citep{Doyle_1990_FeedbackControlTheory}. 
It follows by direct calculation  that:
\aln{K(\z)&=\underbrace{G_o(\z)^{-1}}_{IIR}\underbrace{\left(-c_z^{-1}\z^{-N} +  (1-c_z^{-2})c_z \sum^N_{i=1}(\z^{i-N}/c_z^i) \right)}_{FIR},\nonumber
\intertext{and that:}
\nrm{E(\z)}_2&=\frac{1}{\left|c_z^{N+1}\right|}\sqrt{c_z^2-1}.\label{eqn:H2normsimple}}
%

Since $\nrm{E(\z)}_2\rightarrow 0$  as $N\rightarrow \infty$, we conclude that in this example preview action can overcome completely the tracking limitation
imposed by the {NMP} zero. The optimal controller contains a high-order {FIR} part and a low-order {IIR} part, where the preview action comes from the {FIR} part. The dynamics of the {FIR} block is  fully specified by the {RHP} zero, $c_z$, and the preview length, $N$. The fact that the high order part of the controller is FIR leads to an efficient hardware implementation.
%A similar structure is also observed in the solution to the synthesis problem of Figure~\ref{fig:DistRejSys}, and leads to an efficient implementation of the high-order controller.

A pole-zero plot of the optimal controller is given in Figure \ref{fig:PZforSISOPrevH2} for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(\z-0.5)$, and $N=20$. Notice the almost pole-zero cancellation on the real axis. In the limit $N\rightarrow \infty$ cancellation occurs. 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\columnwidth]{./diags/SimpleExamplePZPlot2.eps}
\end{center}
\caption{Pole-zero plot of the $\htwo$-optimal $K(\z)$ for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(z-0.5)$ and $N=20$.   }
\label{fig:PZforSISOPrevH2}
\end{figure}
This simple preview problem highlights several important features that will be carried over into the more complex problem treated in this paper. In particular:
\begin{enumerate}
\item The preview action is captured in an {FIR} block having order $N$.
\item The remainder of the controller (the {IIR} part) has order equal to the plant order.
\item The preview length (N) required to achieve 95\% (for example) of the maximum norm reduction due to preview, is affected by the position of {NMP} zeros. 
\end{enumerate}

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, an example similar to Figure \ref{fig:SimpleSISOPrevexample} is treated in continuous-time, and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent is: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the continuous-time zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

@@

At this stage, the reader might be left with the impression that preview is of no benefit for {MP} plants. However, as an example, it can be shown that the minimum achievable $\htwo$-norm of the transfer function:
\als{
\ma{E(\z)\\\rho K(\z)}
,}
is reduced by preview action, even when $G(\z)$ is {MP}. By adding the additional term $\rho K(\z)$ into the optimisation,
we are effectively penalising the magnitude of the control action. In general, a large $\rho$ leads to a slow response and so a large $N$ is required in order to get the full benefit from preview action. A detailed analysis of the effects of preview on systems of this form is given in \cite[Chapter 4]{Hazell_2007_Thesis}

>>>>

\label{sec:Intro}
There are many situations in which reference signals, or future disturbances are `previewable'. 
Optimal Preview Control is concerned with designing controllers that exploit previewed information in order to achieve performance levels that are superior to those achievable using current information alone. This paper considers the generic preview synthesis problem illustrated in Figure \ref{fig:DistRejSys}, which comprises a two-degree-of-freedom controller and both previewed disturbances/references ($r$), and unpreviewed disturbances ($w$).
An $\htwo$-optimal solution to this controller synthesis problem is provided that requires only low-dimensional computations and low-dimensional Riccati equation solutions, and leads to a controller whose high-dimensional component is a Finite Impulse Response (FIR) filter; the efficient implementation of FIR filters is well known is the signal processing literature.
The low-dimensional solution to the problem described in Figure~\ref{fig:DistRejSys} derives from the fact that the states of the (high-dimensional) delay line can be reconstructed by making a copy of $\Phi$ in the controller.  The objective of this paper is to provide a framework for synthesizing preview controllers for any problem that fits into the framework illustrated in Figure~\ref{fig:DistRejSys}. In addition, we aim to provide some general insights into the design of preview controllers, and a method for assessing the effectiveness of preview in terms of the achievable $\htwo$-norm reduction.
\begin{figure}
\begin{center}
\stdcontrolfrags
\psfrag{Phi}{$\Phi$}
\psfrag{r}{$r$}
\psfrag{rhat}{$\hat r$}
\psfrag{eta}{$\eta$}
\psfrag{G_p}{$G_p$}
\includegraphics[height=4.0cm]{./diags/DistRejSys.eps}
\caption{\label{fig:DistRejSys} A generalized regulator problem with both previewable and non-previewable disturbances. The transfer function $G$ is the system to be controlled, $K$ is the controller to be synthesized and $\Phi = I \z^{-N}$ is an $N$-step delay line. The disturbance $w$ is not previewable, the control and measurement signals are $u$ and $y$ respectively, $\hat r$ is the previewable disturbance, and $r$ is the future value of $\hat r$. The filter $W_r$ is used  model the expected frequency content of $r$.}
\end{center}
\end{figure}

@@

Figure~\ref{fig:SimpleSISOPrev} illustrates a simple example that may be used to highlight the benefit of preview, the broad structure of the controller, and the effect of preview on the achievable $\htwo$-norm of the closed-loop system. The preview action arises from the delay line $\Phi$. The input to the controller is $r$, which is the future value of the reference, and $K$ is chosen so as to ensure that $e$ is `small', and hence the plant output follows $\Phi r$ as closely as possible. 
\begin{figure}
\stdcontrolfrags
\begin{center}
\includegraphics[width=0.4\hsize]{./diags/SimpleExampleNominalNoK2.eps}
\end{center}
\caption{A simple SISO open-loop preview tracking problem. The transfer function $\Phi=\z^{-N}$ is an $N$-step delay, $G$ is the plant to be controlled, and $K$ is a feedforward controller. The signal $r$ is the \textit{future} value of the reference, and $e$ is the tracking error.}
\label{fig:SimpleSISOPrev}
\end{figure}
%
Define the error system:
\als{E(\z)=G(\z)K(\z)-\Phi(\z),}
and assume that $G(\z)$ is stable; in the case that $G(\z)$ is unstable, it could be replaced by $\hat G(\z)=G(\z)(1-G(\z)K_f(\z))^{-1}$ in which $K_f(\z)$ is a stabilising feedback controller. Providing that $G(\z)$ has all its zeros inside the unit circle, perfect tracking ($E(\z)=0$) may be achieved by simply setting $K(\z)=G(\z)^{-1}\Phi(\z)$. 
However, if $G(\z)$ is nonminimum phase (NMP), then such a $K(\z)$ is not internally stabilising and a controller must be found that recognises the limits imposed by {NMP} zeros on the achievable tracking performance. %Such limitations are well known for non-preview systems (i.e. $N=0$ and $\Phi=1$), and are investigated in some detail in \cite{Middleteon_2004_PrevPerf} and \cite{Mirkin_2004_FixedLagPerfSaturation} for the preview case.

For the case where $G(\z)$ is an arbitrary stable rational transfer function having a single real {NMP} zero at $c_z$, the $\htwo$-optimal controller is easily found. Our objective is to find an internally stabilising $K(\z)$ such that $\nrm{E(\z)}_2$ is minimised.

The following inner-outer factorization  may be performed:
\als{G(\z)&= G_o(\z) G_i(\z),
\intertext{where: }
G_i(\z)&=\frac{\z-c_z}{1-\z c_z}
.}
We can write $E(\z)= (\tilde{K}(\z) -\Phi(\z)G_i(\z^{-1}))G_i(\z)$ in which $\tilde{K}(\z)= K(\z) G_o(\z)$ with
\mbox{$G_i(\z^{-1})G_i(\z)=1$}. The optimal controller is found by setting $K(\z) = (\Phi(\z)G_i(\z^{-1}))_+ G_o^{-1}(\z) $, where $(\cdot)_+$ denotes the stable projection \citep{Doyle_1990_FeedbackControlTheory,LimebeerGreen}. 
It follows by direct calculation  that:
\aln{K(\z)&=\underbrace{G_o(\z)^{-1}}_{IIR}\underbrace{\left(-c_z^{-1}\z^{-N} +  (1-c_z^{-2})c_z \sum^N_{i=1}(\z^{i-N}/c_z^i) \right)}_{FIR},\nonumber
\intertext{and that:}
\nrm{E(\z)}_2&=\frac{1}{\left|c_z^{N+1}\right|}\sqrt{c_z^2-1}.\label{eqn:H2normsimple}}
%

Since $\nrm{E(\z)}_2\rightarrow 0$  as $N\rightarrow \infty$, we conclude that in this example preview action can overcome completely the tracking limitation
imposed by the {NMP} zero. The optimal controller contains a high-order {FIR} part and a low-order infinite impulse response {IIR} part, where the preview action comes from the {FIR} part. The dynamics of the {FIR} block is  fully specified by the {RHP} zero, $c_z$, and the preview length, $N$. The fact that the high order part of the controller is FIR leads to an efficient hardware implementation.
%A similar structure is also observed in the solution to the synthesis problem of Figure~\ref{fig:DistRejSys}, and leads to an efficient implementation of the high-order controller.

A pole-zero plot of the optimal controller is given in Figure \ref{fig:PZforSISOPrevH2} for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(\z-0.5)$, and $N=20$. Notice the almost pole-zero cancellation on the real axis. In the limit $N\rightarrow \infty$ cancellation occurs. 
\begin{figure}
\begin{center}
\includegraphics[width=8cm]{./diags/SimpleExamplePZPlot2.eps}
\end{center}
\caption{Pole-zero plot of the $\htwo$-optimal $K(\z)$ for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(z-0.5)$ and $N=20$.   }
\label{fig:PZforSISOPrevH2}
\end{figure}
This simple preview problem highlights several important features that will be carried over into the more complex problem treated in this paper. In particular:
\begin{enumerate}
\item The preview action is captured in an {FIR} block having order $N$.
\item The remainder of the controller (the {IIR} part) has order equal to the plant order.
\item The preview length (N) required to achieve 95\% (for example) of the maximum norm reduction due to preview, is affected by the position of {NMP} zeros. 
\end{enumerate}

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, an example similar to Figure \ref{fig:SimpleSISOPrev} is treated in continuous-time, and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent of this result is: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the continuous-time zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications or unstable poles (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

@@

At this stage, the reader might be left with the impression that preview is of no benefit for minimum phase {MP} systems. However, as an example, it can be shown that the minimum achievable $\htwo$-norm of the transfer function:
\als{
\ma{E(\z)\\\rho K(\z)}
,}
is reduced by preview action, even when $G(\z)$ is {MP}. By adding the additional term $\rho K(\z)$ into the optimisation,
we are effectively penalising the magnitude of the control action. In general, a large $\rho$ leads to a slow response and so a large $N$ is required in order to get the full benefit from preview action. A detailed analysis of the effects of preview on systems of this form is given in \cite[Chapter 4]{Hazell_2007_Thesis}
